A user-extensible and adaptable parser architecture

### 2008-05-26 papers/sgai-2008/paper.tex
Use Springer's bibliography style.
Added graph showing distribution of rules per action. Some other minor changes.

@@

XXX FORMAT OF REFERENCES\@.

@@

Existing parsers were considered, but their parsing coverage was too low,
their parsing too inexact, and/or they did not extract sufficient data for
the purposes of this project.\footnote{A review of the existing parsers
considered for this project will be included in the thesis.} The effort
required to adapt and improve an existing parser was judged to be greater
than the effort to write one from scratch, as the techniques used by the
existing parsers severely limited their potential: some ignored the
majority of log lines, parsing specific log lines with great accuracy, but
in an inextensible fashion; others sloppily parsed the majority of log
lines, but were incapable of distinguishing between log lines of the same
type, e.g.\ rejections, and the data they extracted was constrained to the
\LCD{}.

The solution developed is conceptually simple: provide a few generic functions,
each capable of dealing with an entire \textit{category\/} of log lines (e.g.\
rejections), accompanied by a multitude of precise patterns, each of which
matches all log lines of a specific type, and only that type (e.g.\ rejection
by a specific \RBL{}).

@@

Explain adding new rules and actions.  Cut down rule attributes to the
minimum possible.

@@

The framework provides utility and support functions for the actions and
rules.  It provides shared storage to pass data between actions, most
notably the data structures used to represent each connection and mail,
though there are some others.  It loads and validates rules, controls
parsing of log files, invoking actions and tracking performance data, and
stores results on request.

The function which finds the rule matching the input line and invokes the
requested action can be expressed in pseudo-code (with indentation denoting
flow-of-control) as:

@@

Actions contain the code required to deal with log lines from a particular
category, e.g.\ rejections.

@@

\bibliographystyle{../common/bibliography-style}
\bibliography{../common/bibliography}
\label{bibliography}

>>>>

\newcommand{\numberOFlogFILES}[0]{%
    93%
}

\newcommand{\numberOFrules}[0]{%
    169%
}

\newcommand{\numberOFlogLINES}[0]{%
    60,721,709%
}

\newcommand{\numberOFlogLINEShuman}[0]{%
    60.72 million%
}

\newcommand{\numberOFactions}[0]{%
    18%
}

@@

@@

Existing parsers were considered, but their parsing coverage was too low,
their parsing too inexact, and/or they did not extract sufficient data for
the purposes of this project.\footnote{A review of the existing parsers
considered for this project will be included in the thesis.} The effort
required to adapt and improve an existing parser was judged to be greater
than the effort to write one from scratch, as the techniques used by the
existing parsers severely limited their potential: some ignored the
majority of log lines, parsing specific log lines with great accuracy, but
in an inextensible fashion; others sloppily parsed the majority of log
lines, but were incapable of distinguishing between log lines of the same
type, e.g.\ rejections, and they extracted only a portion of the data
required for this project.

The solution developed is conceptually simple: provide a few generic functions,
each capable of dealing with an entire \textit{category\/} of log lines (e.g.\
rejections), accompanied by a multitude of precise patterns, each of which
matches all log lines of a specific type, and only that type (e.g.\ rejection
by a specific \RBL{}).  XXX STOP \RBL{} BEING EXPANDED AGAIN\@.

@@

Explain adding new rules and actions.

@@

The framework provides utility and support functions for the actions and
rules.  It provides shared storage to pass data between actions, most
notably the data structures used to represent each connection and mail,
though there are some others.  It loads and validates rules, controls
parsing of log files, invoking actions and tracking performance data, and
stores results in the database on request.  The framework is independent of
the parser being written: the same functionality will be required from the
framework for most or all parsers.

The function which finds the rule matching the input line and invokes the
requested action can be expressed in pseudo-code (with indentation denoting
flow of control) as:

@@

Actions contain the code required to deal with log lines from a particular
category, e.g.\ rejections.  The actions are parser-specific: each parser
will need to write the actions it requires from scratch, unless it's
extending an existing parser.  In the Postfix parser developed for this
project there are \numberOFactions{} actions and \numberOFrules{} rules.

\showgraph{build/plot-action-distribution}{Distribution of rules
per action}{Distribution of rules per action}

@@

\bibliographystyle{spmpsci}
\bibliography{../common/bibliography}
\label{bibliography}
